IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/intro.tex
intro pass

Information flow control (IFC) is a promising technique
that provides security
by tracking the flow of sensitive data through a system.
Untrusted code is confined so that it cannot exfiltrate data, except as
per an information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in dynamic information
flow control is implementation efficiency: when
information flow is tracked at a fine-grained level,
e.g., per value in the system, systems may incur
impractical runtime overhead.

In the alternative \textit{coarse-grained} approach to IFC,
a system is divided into relatively course computational units,
each with a single label dictating its security policy.
Only
communication between isolated computational units must be tracked.
A recent system named SWAPI adds IFC to the
browser by identifying \emph{web workers} as an existing computational
unit.  Communication between workers is mediated using
IFC to ensure non-interference, preventing sensitive workers from
influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages:
(1) reduced runtime overhead because checks need only
be performed at isolation boundaries, (2) minimal changes to an
existing programming language when adding IFC, which (3) allows
the reuse of existing programs.  Finally, (4) associating
a single security label with the entire computational unit simplifies
understanding and easy reasoning about the correctness of the
system, without information-flow reasoning about the
technical details of the semantics of the programming language.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notation of clearance. (Section~\ref{sec:extensions})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for Javascript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We informally relate our results to a monadic interpretation
      of IFC which guided our design. (Section~\ref{sec:monad})     
\end{itemize}

>>>>

Information flow control (IFC) is a promising technique
that provides security
by tracking the flow of sensitive data through a system.
Untrusted code is confined so that it cannot exfiltrate data, except as
per an information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in dynamic information
flow control is implementation efficiency: when
information flow is tracked at a fine-grained level,
e.g., per value in the system, systems may incur
impractical runtime overhead~\cite{JSFlow}.
%
Moreover, the task of adding fine-grained IFC event to a simple language is
non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
such as JavaScript, this challenge is becomes almost insurmountable.

In the alternative \textit{coarse-grained} approach to IFC,
a system is divided into relatively course computational units,
each with a single label dictating its security policy.
Only
communication between isolated computational units must be tracked.
A recent system named SWAPI adds IFC to the
browser by identifying \emph{Web workers} as an existing computational
unit~\cite{swapi}.  Communication between workers is mediated using
IFC to ensure non-interference, preventing sensitive workers from
influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages:
(1) reduced runtime overhead because checks need only
be performed at isolation boundaries, (2) minimal changes to an
existing programming language when adding IFC, which (3) allows
the reuse of existing programs.  Finally, (4) associating
a single security label with the entire computational unit simplifies
understanding and easy reasoning about the correctness of the
system, without information-flow reasoning about the
technical details of the semantics of the programming language.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for Javascript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notation of clearance. (Section~\ref{sec:extensions})
  \item We informally relate our results to a monadic interpretation
      of IFC which guided our design. (Section~\ref{sec:monad})     
\end{itemize}
